Towards the Analysis of the Queuing System Operating in~the~Random Environment with Resource Allocation

### 2020-09-24 template/preamble/font/fontspec/dejavu-condensed.tex

\newfontfamily\cyrillicfont[Script=Cyrillic,Ligatures=TeX]{DejaVu Serif}
\newfontfamily\cyrillicfontsf[Script=Cyrillic,Ligatures=TeX,Scale=MatchUppercase]{DejaVu Sans}
\newfontfamily\cyrillicfonttt[Script=Cyrillic,Scale=MatchUppercase]{DejaVu Sans Mono}

\setmainfont[Ligatures=TeX]{DejaVu Serif}
\setsansfont[Ligatures=TeX,Scale=MatchUppercase]{DejaVu Sans}
\setmonofont[Scale=MatchLowercase,Scale=MatchUppercase]{DejaVu Sans Mono}

>>>>

\newfontfamily\cyrillicfont[Script=Cyrillic,Ligatures=TeX]{DejaVu Serif Condensed}
\newfontfamily\cyrillicfontsf[Script=Cyrillic,Ligatures=TeX,Scale=MatchLowercase]{DejaVu Sans Condensed}
\newfontfamily\cyrillicfonttt[Script=Cyrillic,Scale=MatchUppercase]{DejaVu Sans Mono}

\setmainfont[Ligatures=TeX]{DejaVu Serif Condensed}
\setsansfont[Ligatures=TeX,Scale=MatchLowercase]{DejaVu Sans Condensed}
\setmonofont[Scale=MatchLowercase,Scale=MatchUppercase]{DejaVu Sans Mono}
